---
title: "Intro to Exploding Boxplots"
author: "Kenton Russell"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Intro to Exploding Boxplots}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

[Exploding Boxplots](https://github.com/mcaule/d3_exploding_boxplot) provide a fun and useful look at the distribution of data.  This `R` package [`explodingboxplotR`](https://github.com/timelyportfolio/explodingboxplotR) uses `htmlwidgets` to allow us to incorporate these exploding boxplots in all R contexts, such as `rmarkdown`, `Shiny`, the `R` console, and in a web browser.

### Install

`explodingboxplotR` is not on CRAN, so we'll use `devtools::install_github` to install.

```{r eval = FALSE}
devtools::install_github("timelyportfolio/explodingboxplotR")
```

### Use

```{r}
library(explodingboxplotR)

# use this to replicate
#   from ?boxplot
#boxplot(count ~ spray, data = InsectSprays, col = "lightgray")

exploding_boxplot(
  data.frame(
    rowname = rownames(InsectSprays),
    InsectSprays,
    stringsAsFactors = FALSE
  ),
  y = "count",
  group = "spray",
  color = "spray",
  label = "rowname"
)
```

We get some options to customize our exploding boxplots.  Let's look at these in the next example.

```{r}
# demonstrate all of the options
#  xlab does not work
#  filed issue on source repo
exploding_boxplot(
  data.frame(
    rowname = rownames(InsectSprays),
    InsectSprays,
    stringsAsFactors = FALSE
  ),
  y = "count",
  group = "spray",
  color = "spray",
  label = "rowname",
  iqr = 2,
  margin = list(bottom = 50, left = 30, top = 20, right = 20),
  xlab = "Spray Type",
  ylab = "Count Provided"
)
```
